Characterization of an anionic membrane mimetic with natural phospholipid content and magnetic orienting capabilities

### 2020-09-08 article.tex
Typos corregidos

	\renewcommand{\thefootnote}{\alph{footnote}}
	\section{Introduction}
	The cell is a highly complex unit present in all living organisms: it
	constitutes the building block of life. Essentially, consists in a closed
	domain
	containing smaller organelles in a highly complex and crowded aqueous solution,
	all enclosed by a bilayer made of mainly phospholipids among other lipids and
  also containing sugars, cholesterol and proteins, among others. This bilayer is called
	cell membrane or cytoplasmic membrane. Membranes itself are very complex
	molecular organizations with variable and inhomogeneous composition, and its
	atomic level understanding is a very difficult task. For this reason, the
	employment of
	membrane mimetics and models has become common practice.\cite{Bondar2019}\\
	Because of their ability to orient spontaneously when exposed to an external
	magnetic field, bilayered micelles, also called ``bicelles'', have been widely
	used as membrane mimetics, as they allow the use of solution NMR to probe the
	orientation and dynamics of liposomes and
	drugs\cite{Beaugrand2016,Montecinos2007,Ruiz-Fernandez2016}. Although a
	composition capable of forming magnetic orienting bicelles was described in the
	late 1960s\cite{Lawson1967}, the authors did not recognize the bicelle structure
	at the time, instead, ten years later Amaral \textit{et al.} were the first to
	identify the bicelle structure
	with a mixture of sodium decyl sulphate and
	1-decanol\cite{Amaral1979}. Later,
	in the 1990s, it was discovered that a
	mixture of DMPC\footnote{1,2-dimyristoyl-\textit{sn}-glycero-3-phosphocholine}
	and
	CHAPSO\footnote{3-(cholamidopropyl)dymethylammonio-2-hydroxy-1-propanesulfonate}
	forms magnetically orientable bicelles\cite{Sanders1990}, these aggregates are
	suitable to use as a membrane mimetics, as they contain
	phospholipid in their composition. Many improvements have been made to this
	composition over the years. It was found that CHAPSO can be replaced by
	DHPC\footnote{1,2-dihexanoyl-\textit{sn}-glycero-3-phosphocholine} which has a
	structure that resembles more to a natural phospholipid\cite{Sanders1992}, it
	was also found
	that the addition of cholesterol improves the stability of the
	bilayer\cite{Shapiro2010} and
	the addition of Triton X-100 detergent improves its magnetic orienting
	capabilities\cite{Park2010}. Nowadays, bicelles are considered good membrane
	mimetics, as they have been successfully employed to predict drug permeability
	through the membrane\cite{Sun2008,Durr2013,Matsumori2007,Koenig2005}, and to
	elucidate
	protein structures in the trans-membrane domain\cite{Durr2012}. The use of
	bicelles is ideal when
	the
	drug-detergent (or protein-detergent) complex is small (<\SI{100}{kDa}), as
	these systems can be studied in solution
	NMR\cite{Warschawski2011,Raschle2010,Sanders2006}. However, it should be
	pointed out that a single phospholipid bilayer by no means represents the
	complexity of the mixture found in natural membranes.\\

@@

	%channel\cite{Oakes2019,Martin2014,Shibata2005,Griepernau2007,EmmaTerama2008,DePaula2008,Cantor1998,Bernardi2009,Godwin2005}.
	% Despite which mechanisms are actually taking place, crossing membrane
	%interfaces
	% to become incorporated into the hydrophobic domain appears to be a crucial
	%step
	% for
	% most drugs.\\
	Benzocaine is a well-known local anesthetic for topical use. It has been widely
	employed anesthetizing the oropharynx for trans-esophageal echocardiography,
	bonchoscopy, esophagogastroduodenoscopy, in cold sores, mouth ulcers,
	toothache,
	sore gums and denture ache among others\cite{McEvoy2007}.
	% A significant number of
	% cases of Benzocaine induced cyanosis (methemoglobinemia) have been reported
	% along the
	% years\cite{Lardieri2019}, however it still remains in use.\\
	Benzocaine has been subject of a significant number of studies, including free
	energy transfer from water to the interior of different membrane
	mimetics\cite{Martin2014a,Cascales2011,Porasso2009,J.J.LopezCascales2006},
	estimations about location and orientation in different bilayers and
	monolayers\cite{Matsuki2001,Suwalsky2004,Kuroda2000,Choi2001}, interactions
	with
	a variety of
	solvents\cite{Cardenas2016,Cardenas2018,Paluch2015,Avila2002,Aguado2013} and
	encapsulation in different structures for controlled delivery
	purposes\cite{Shkurenko2018,AttouiYahia2017,Li2016,Arantes2014,Puglia2011}
	among
	others. All the evidence confirms that Benzocaine is able to cross the
	interface
	of membrane mimetics to become incorporated into the
	hydrophobic bilayer to finally be located along the first carbons of the
  aliphatic chains, remaining close to the interface at equilibrium. \\
	Contrary to most local anesthetics, Levodopa (or L-DOPA), the precursor of the
	neurotransmitter dopamine, commonly used in treatment of Parkinson's
	disease\cite{Fabbrini1987},
	is
	able to cross membrane interfaces only via active
	processes\cite{BENTLEY2012349,PRYOR2013180}.
	Therefore, in the absence of appropriate specific receptors, Levodopa should
	remain attached to the outer interface and should not reach the hydrophobic
	bilayer core\cite{Orowski2012}.\\

	In this article, we present a new anionic nematic lyotropic liquid crystal,
	with bilayer structure, susceptible to be used as membrane mimetic. It is made
	of sodium dodecyl sulfate (SDS), 1-decanol (DeOH), sodium sulphate
	(\ce{Na2SO4})
	and a mixture of natural phospholipids extracted from soybean, all dissolved in
	water. The structure of the mesophase, which spontaneously orients in magnetic
	fields,
	was characterized using polarized light microscopy textures and to observe the
	dynamics
	of the interface as well as deeper into the hydrophobic core, $^2$H-NMR
	quadrupole splittings from HDO, DeOH-$\alpha$-d$_2$, and SDS-d$_{25}$ were
	measured. To test the capability of the new mimetic to reproduce
	cell membrane behavior, Benzocaine ($\log P_{\nicefrac{O}{W}} = 2.12$\todo{ G.R. Strichartz, V. Sanchez, R. Arthur, R. Chafetz, D. Martin,Anesth.  Analg.  71  (1990)  158.}) and Levodopa ($\log P_{\nicefrac{O}{W}} = -2.39$\todo{Sangster, J., 1993. “Log Kow Databank”, Sangster Res. Lab.Montreal, Quebec, Canada.}) were dissolved in the mesophase
	solution. According to previous evidence, Benzocaine should spontaneously be
	incorporated inside the bilayer and become located around the first carbons of
  the aliphatic chains\cite{Martin2014a},
	whereas Levodopa should remain along the Stern layer of the interface without
  entering the bilayer\cite{Orowski2012}. 
	To obtain an atomic detailed characterization of the mimetic dynamics and
	structure, including information about location, interface crossing dynamics
	and
	interactions of Benzocaine and Levodopa with the bilayer components, the
	spectroscopic measurements were complemented with classical molecular dynamics
	(MD) simulations.

@@

	\subsection{Nuclear magnetic resonance}
	\label{sec:method_nmr}
	All solution $^2$H-NMR experiments were carried out on a Bruker Avance 400
	spectrometer (Universidad de Santiago de Chile, Santiago, Chile) operating at
	\SI{61.422}{MHz}. Spectra were obtained with a $\pi/2$ pulse length of
	\SI{22.4}{\micro\second}, an acquisition time of \SI{760}{ms}, an spectral
	width of \SI{43.1}{kHz} in \SI{32}{kb} files with a digital resolution of
	\SI{1.32}{Hz} per point.
	256 scans were acquired per spectrum. Spectra
	were acquired at \SI{37}{\celsius}, and a 10 minute pre-acquisition delay was
	employed to allow each sample to reach thermal equilibrium. Spectra were
	processed
	using Bruker TopSpin 4.0 software.

@@

	MD calculations were performed in the National Laboratory for High Performace
	Computing (Universidad de Chile, Santiago, Chile).
	All simulations were performed using the GROMACS-2016\cite{Abraham2015}
	software
	bundle. A cutoff scheme was used for non-bonding interactions according to each
	force-field recommendation values, and long range electrostatic interactions
	were calculated employing the particle mesh Ewald method\cite{DiPierro2015}.
	Temperature control was achieved with a modified Berendsen
	thermostat\cite{Bussi2007} with a time constant of \SI{1.0}{ps}, while pressure
	was equilibrated with a semi-isotropic Berendsen barostat\cite{Berendsen1984}
	with a time constant of \SI{1.0}{ps} for both xy-plane and z-axis. Both,
	temperature and pressure were adjusted to \SI{310}{K} and \SI{1}{bar}
	respectively. Periodic
	boundary conditions were applied on all three dimensions.\\ Several force
	fields were tested.
	Before each production simulation, a short equilibration run was performed for
	a
	duration of \SI{1}{ns} with an integration time-step of \SI{1}{fs}. Afterwards,
	each production run was calculated to a duration of \SI{40}{ns} with an
	integration time-step of \SI{2}{fs}. TIP3P water
	model\cite{Neria1996,Jorgensen1983} was employed on the
	simulation with CHARMM36 force-field, while SPC/E\cite{Berendsen1987} was
	employed on simulations
	with Berger and Gromos53A6 force-fields. The same initial configuration was
	employed to test each force-field, and it was generated using software
	Packmol\cite{Martinez2009} arranging a bilayer with composition in the same
	proportion as the membrane mimetic in table \ref{tab:mimetic_composition} to a
	total of 9613 molecules. The phospholipid mixture was simulated as a mixture of
	39\%
	PLPC\footnote{1-palmitoyl-2-linoleoyl-\textit{sn}-glycero-3-phosphocholine},
	26\% DLPC\footnote{1,2-dilinoleoyl-\textit{sn}-glycero-3-phosphocholine}, 24\%
	DLPE\footnote{1,2-dilinoleoyl-\textit{sn}-glycero-3-phosphoethanolamine} and
	11\% DOPE\footnote{1,2-dioleoyl-\text{sn}-glycero-3-phosphoethanolamine}. These
	proportions were chosen in accordance with the composition of the phospholipid
	mixture employed, as
	reported by the vendor.\\
	PMF calculations were performed employing the Umbrella Sampling/WHAM
	method\cite{Kumar1992}. The starting configuration of each simulation window
	employed for the PMF calculation was generated from a trajectory of the target
	molecule pulling away from the center of the bilayer, making a starting point
	each \SI{1.5}{\angstrom}, up to \SI{4.5}{nm} making a total of 30 simulation
	windows. Each simulation window was calculated with the same parameters as the
	calibrated model shown ahead, up to a total of \SI{20}{ns} on each window, with
	a weak harmonic force with constant
	\SI{240}{\kilo\joule\per\mole\per\nano\meter\squared} applied on the bilayer
	in order to maintain its shape and position during the course of each
	simulation window.\\

@@

	Another condition that the mimetic must fulfill, is that the magnetic susceptibility of the mesophase of the mimetic must be anisotropic so it can orient itself when exposed to an external magnetic field. This is so the
  deuterated probes in the mimetic can produce a \textit{quadrupole splitting}
  in a solution $^2$H-RMN spectrum, which will be used to calibrate the MD
  simulations. This calibrated simulation can be used to assess other
  properties, not possible to measure experimentally, with more
	confidence.\\

@@

	In order to obtain more reliable information from a molecular dynamic
	simulation,
	it is desirable that experimentally measured properties are well reproduced by
	calculations. That said, MD has to be calibrated to reproduce known experimental
	results, which is why
	we
	tested multiple force-fields to see which one yields a closer representation of
	the aliphatic chain dynamics, evidenced by reproducing $^2$H-RMN quadrupole
	splittings. Figure \ref{fig:reference}-A shows the $^2$H-NMR spectrum of the
	membrane mimetic prepared according to the composition stated in table
	\ref{tab:mimetic_composition}, enriched with \ce{D2O}(0.5\% of the total
	\ce{H2O} replaced by \ce{D2O}) and SDS-d$_{25}$(10\% of the total SDS replaced
	by SDS-d$_{25}$). The quadrupolar splitting of each C-D bond depends largely on
	their order parameter ($S_{CD}$, see equation \ref{eq:splitting}), therefore it
	makes sense to assign each quadrupolar splitting from the least ordered to the
	most ordered methylene, resulting as follows: The central signal arises from an
	average in time of HDO oriented at the interface in fast exchange with
	non-oriented HDO at the bulk (smallest splitting, \SI{388}{Hz}. Not shown). The
	next less split signal arises from the deuterated methyl group (\ce{CD3}-)
	capping the tail of each SDS-d$_{25}$, as the rotation of this group produces a
	lower order parameter, the smallest along the chain. The rest of the more split
	signals correspond to subsequent deuretated methylenes (-\ce{CD2}-), with the
	ones closer to the charged sulphate head-group having a higher quadrupolar
	splitting, since the strong Coulombic interaction between this charged end and
	the interface produces a restraining effect on the movement of the nearby
	deuterons. The adjustment of the simulation relies on the accurate reproduction
	of these quadrupolar splittings from SDS-d$_{25}$, as they reflect the dynamics
	of the lipid chains in the bilayer.\par
	\begin{figure}[h]
		\centering
		\includegraphics[width=\columnwidth]{nmr_reference.pdf}
		\caption{$^2$H-NMR spectrum of: (A) membrane mimetic enriched with SDS-d$_{25}$.
			Central peak (not shown completely) belongs to \ce{HDO} present in the
			sample, while the rest of the signals are split SDS-d$_{25}$ signals which
			were used as reference to calibrate a computational model. (B) DMPC/DHPC bicelle with added cholesterol and polyinsaturated phospholipids and enriched with DMPC-d$_{54}$ (R.E. Minto \textit{et al.}, Chem. Phys. Lipids 132 (2004) 55–64)}
		\label{fig:reference}
	\end{figure}
	Initially,
	three force-fields with different partial charge distributions were tested.
	These force-fields were chosen due to their ability to reproduce other
	structures of
	SDS aggregates\cite{Tang2014}.\par
	The tested force-fields were:
	\begin{itemize}
		\item CHARMM36\cite{Vanommeslaeghe2009}
		\item Berger\cite{Berger1997} with partial charge distribution according to
		Merz-Kollman
		method\cite{Besler1990}
		\item Berger with partial charge distribution according to
		Gromos53A6\cite{Oostenbrink2004}
		parameters.
		\item Gromos53A6 with partial charge distribution according to Merz-Kollman
		method.
		\item Gromos53A6 with partial charge distribution according to its own
		parameters.
	\end{itemize}

@@

	Further improvement to the fitting of predicted splittings was done by
	employing
	two thermostats in the simulation, one governing the bulk solution with a
	reference temperature of \SI{310}{K} and another governing the bilayer
	components with a reference temperature of \SI{320}{K}, a little higher to
	introduce more kinetic energy to the chains. The reasoning behind
	this decision was based on the expectation that increased velocity on the
	bilayer components would have a greater effect on the mobility towards the
	center on the bilayer rather than in the interface, where Coulombic
	interactions
	are stronger and have a restraining effect on the mobility of the bilayer.
	After
	this adjustment, the simulation results in predicted quadrupolar splittings in
	very good agreement with the experimental ones, as shown in figure
	\ref{fig:2nd_calibration}.

@@

	Polarized light microscopy of the mesophase shows a thread-like pattern, this
	is
	characteristic of a lyotropic nematic phase\cite{dierking2006textures}.
	Furthermore, considering the magnitude of the measured quadrupolar
	splittings, and the fact that each methylene's deuteron pair in SDS-d$_{25}$
	yields
	a
	single quadrupolar splitting in solution $^2$H-NMR (see figure
	\ref{fig:reference}-A), we can conclude that this phase has a bilayer
	like structure with its bilayer normal perpendicular
	to the magnetic field ($\theta=\pi/2$ in eq. \ref{eq:splitting}). The
	posibility of a calamitic phase is discarded, since a calamitic phase implies a
	director axis being parallel to the magnetic field ($\theta=0$ in eq.
	\ref{eq:splitting}) which would produce splittings considerably smaller than
	observed. Regarding the size of the aggregate, cryo-TEM imagery of similar
  bicelles (made with TTA\footnote{Trimethyltetradecylammonium} instead of SDS)
  results in aggregates of about
  \SI{2}{nm}-\SI{5}{nm}\todo{RSCAdv.,2016,6,7455}, and we expect for the size of
  the membrane mimetic aggregate to be in the same order of magnitude.\\
   When comparing the NMR spectrum of this bicelle (figure \ref{fig:reference}-A) with one taken from a DHPC/DMPC bicelle with cholesterol and polyinstaturated phospholipids (figure \ref{fig:reference}-B)\todo{R.E. Minto \textit{et al.}, Chem. Phys. Lipids 132 (2004) 55–64}, one can see that DMPC-d$_{54}$ splittings (and hence order parameters) are similar to the splittings in SDS-d$_{25}$, therefore one can conclude that the orientational dynamics of this SDS-containing mimetic are similar to a mimetic made from purely phospholipid.\\

@@

	When studying the
	effects of adding \SI{7}{mg} of Levodopa per gram of membrane mimetic enriched
	with SDS-d$_{25}$, the effects are minor to negligible (see figure
	\ref{fig:sds_benzocaine}),
	implying that Levodopa is unable to enter the bilayer to alter
	the dynamics of the aliphatic chains.\\
	Employing the same method as in Benzocaine, a PMF profile was calculated for
	the
	process of Levodopa permeating the membrane mimetic (figure
	\ref{fig:levodopa_profile}). This profile shows that the lowest
	energy location for Levodopa to be in, is outside the bilayer, alongside the
	Stern
	layer.
	It also shows that in order to permeate the interface to translocate through
	the mimetic, Levodopa requires a rather
	large activation energy (\SI{102.4}{\kilo\joule\per\mol}), showing that a
	passive permeation of Levodopa mechanism is actually not possible at
	physiological temperature, as confirmed by $^2$H-NMR spectra. 
	\begin{figure}[htb]
		\centering
		\includegraphics[width=\columnwidth]{ldopa_profile_density}    
		\caption{Mean force potential profile for the process of Levodopa
			translocating through a membrane mimetic. The blue dotted area represents
			the water particle density, while the smooth orange area represents the
			lipid particle density in the simulation.}
		\label{fig:levodopa_profile}
	\end{figure}

>>>>

	\renewcommand{\thefootnote}{\alph{footnote}}
	\section{Introduction}
	The cell is a highly complex unit present in all living organisms: it
	constitutes the building block of life. Essentially, consists in a closed
	domain
	containing smaller organelles in a highly complex and crowded aqueous solution,
	all enclosed by a bilayer made of mainly phospholipids among other lipids and
  also containing sugars, cholesterol and proteins, among others. This bilayer is called
	cell membrane or cytoplasmic membrane. Membranes itself are very complex
	molecular organizations with variable and inhomogeneous composition, and its
	atomic level understanding is a very difficult task. For this reason, the
	employment of
	membrane mimetics and models has become common practice.\cite{Bondar2019}\\
	Because of their ability to orient spontaneously when exposed to an external
	magnetic field, bilayered micelles, also called ``bicelles'', have been widely
	used as membrane mimetics, as they allow the use of solution NMR to probe the
	orientation and dynamics of liposomes and
	drugs\cite{Beaugrand2016,Montecinos2007,Ruiz-Fernandez2016}. Although a
	composition capable of forming magnetic orienting bicelles was described in the
	late 1960s\cite{Lawson1967}, the authors did not recognize the bicelle structure
	at the time, instead, ten years later Amaral \textit{et al.} were the first to
	identify the bicelle structure
	from a mixture of sodium decyl sulphate and
	1-decanol\cite{Amaral1979}. Later,
	in the 1990s, it was discovered that a
	mixture of DMPC\footnote{1,2-dimyristoyl-\textit{sn}-glycero-3-phosphocholine}
	and
	CHAPSO\footnote{3-(cholamidopropyl)dymethylammonio-2-hydroxy-1-propanesulfonate}
	forms magnetically orientable bicelles\cite{Sanders1990}, these aggregates are
	suitable to use as a membrane mimetics, as they contain
	phospholipid in their composition. Many improvements have been made to this
	composition over the years. It was found that CHAPSO can be replaced by
	DHPC\footnote{1,2-dihexanoyl-\textit{sn}-glycero-3-phosphocholine} which has a
	structure that resembles more to a natural phospholipid\cite{Sanders1992}, it
	was also found
	that the addition of cholesterol improves the stability of the
	bilayer\cite{Shapiro2010} and
	the addition of Triton X-100 detergent improves its magnetic orienting
	capabilities\cite{Park2010}. Nowadays, bicelles are considered good membrane
	mimetics, as they have been successfully employed to predict drug permeability
	through the membrane\cite{Sun2008,Durr2013,Matsumori2007,Koenig2005}, and to
	elucidate
	protein structures in the trans-membrane domain\cite{Durr2012}. The use of
	bicelles is ideal when
	the
	drug-detergent (or protein-detergent) complex is small (<\SI{100}{kDa}), as
	these systems can be studied in solution
	NMR\cite{Warschawski2011,Raschle2010,Sanders2006}. However, it should be
	pointed out that a single phospholipid bilayer by no means represents the
	complexity of the mixture found in natural membranes.\\

@@

	%channel\cite{Oakes2019,Martin2014,Shibata2005,Griepernau2007,EmmaTerama2008,DePaula2008,Cantor1998,Bernardi2009,Godwin2005}.
	% Despite which mechanisms are actually taking place, crossing membrane
	%interfaces
	% to become incorporated into the hydrophobic domain appears to be a crucial
	%step
	% for
	% most drugs.\\
	Benzocaine is a well-known local anesthetic for topical use. It has been widely
	employed anesthetizing the oropharynx for trans-esophageal echocardiography,
	bonchoscopy, esophagogastroduodenoscopy, in cold sores, mouth ulcers,
	toothache,
	sore gums and denture ache among others\cite{McEvoy2007}.
	% A significant number of
	% cases of Benzocaine induced cyanosis (methemoglobinemia) have been reported
	% along the
	% years\cite{Lardieri2019}, however it still remains in use.\\
	Benzocaine has been subject of a significant number of studies, including free
	energy transfer from water to the interior of different membrane
	mimetics\cite{Martin2014a,Cascales2011,Porasso2009,J.J.LopezCascales2006},
	estimations about location and orientation in different bilayers and
	monolayers\cite{Matsuki2001,Suwalsky2004,Kuroda2000,Choi2001}, interactions
	with
	a variety of
	solvents\cite{Cardenas2016,Cardenas2018,Paluch2015,Avila2002,Aguado2013} and
	encapsulation in different structures for controlled delivery
	purposes\cite{Shkurenko2018,AttouiYahia2017,Li2016,Arantes2014,Puglia2011}
	among
	others. All the evidence confirms that Benzocaine is able to cross the
	interface
	of membrane mimetics to become incorporated into the
	hydrophobic bilayer to finally be located along the first carbons of the
  aliphatic chains, remaining close to the interface at equilibrium. \\
	Contrary to most local anesthetics, Levodopa (or L-DOPA), the precursor of the
	neurotransmitter dopamine, commonly used in treatment of Parkinson's
	disease\cite{Fabbrini1987},
	is
	able to cross membrane interfaces only via active
	processes\cite{BENTLEY2012349,PRYOR2013180}.
	Therefore, in the absence of appropriate specific receptors, Levodopa should
	remain near the aqueous region, and should not reach the hydrophobic
	bilayer core\cite{Orowski2012}.\\

	In this article, we present a new anionic nematic lyotropic liquid crystal,
	with bilayer structure, susceptible to be used as membrane mimetic. It is made
	of sodium dodecyl sulfate (SDS), 1-decanol (DeOH), sodium sulphate
	(\ce{Na2SO4})
	and a mixture of natural phospholipids extracted from soybean, all dissolved in
	water. The structure of the mesophase, which spontaneously orients in magnetic
	fields,
	was characterized using polarized light microscopy textures, and to observe the
	dynamics
	of the interface as well as deeper into the hydrophobic core, $^2$H-NMR
	quadrupole splittings from HDO, DeOH-$\alpha$-d$_2$, and SDS-d$_{25}$ were
	measured. To test the capability of the new mimetic to reproduce
	cell membrane behavior, Benzocaine ($\log P_{\nicefrac{O}{W}} = 2.12$\cite{Strichartz1990}) and Levodopa ($\log P_{\nicefrac{O}{W}} = -2.39$\cite{Sanders1993}) were dissolved in the mesophase
	solution. According to previous evidence, Benzocaine should spontaneously be
	incorporated inside the bilayer and become located around the first carbons of
  the aliphatic chains\cite{Martin2014a},
	whereas Levodopa should remain along the Stern layer of the interface without
  entering the bilayer\cite{Orowski2012}. 
	To obtain an atomic detailed characterization of the mimetic dynamics and
	structure, including information about location, interface crossing dynamics
	and
	interactions of Benzocaine and Levodopa with the bilayer components, the
	spectroscopic measurements were complemented with classical molecular dynamics
	(MD) simulations.

@@

	\subsection{Nuclear magnetic resonance}
	\label{sec:method_nmr}
	All solution $^2$H-NMR experiments were carried out on a Bruker Avance 400
	spectrometer (Universidad de Santiago de Chile, Santiago, Chile) operating at
	\SI{61.422}{MHz}. Spectra were obtained with a $\pi/2$ pulse length of
	\SI{22.4}{\micro\second}, an acquisition time of \SI{760}{ms}, a spectral
	width of \SI{43.1}{kHz} in \SI{32}{kb} files with a digital resolution of
	\SI{1.32}{Hz} per point.
	256 scans were acquired per spectrum. Spectra
	were acquired at \SI{37}{\celsius}, and a 10 minute pre-acquisition delay was
	employed to allow each sample to reach thermal equilibrium. Spectra were
	processed
	using Bruker TopSpin 4.0 software.

@@

	MD calculations were performed in the National Laboratory for High Performace
	Computing (Universidad de Chile, Santiago, Chile).
	All simulations were performed using the GROMACS-2016\cite{Abraham2015}
	software
	bundle. A cutoff scheme was used for non-bonding interactions according to each
	force-field recommendation values, and long range electrostatic interactions
	were calculated employing the particle mesh Ewald method\cite{DiPierro2015}.
	Temperature control was achieved with a modified Berendsen
	thermostat\cite{Bussi2007} with a time constant of \SI{1.0}{ps}, while pressure
	was equilibrated with a semi-isotropic Berendsen barostat\cite{Berendsen1984}
	with a time constant of \SI{1.0}{ps} for both xy-plane and z-axis. Both,
	temperature and pressure were adjusted to \SI{310}{K} and \SI{1}{bar}
	respectively. Periodic
	boundary conditions were applied on all three dimensions.\\ Several force
	fields were tested.
	Before each production simulation, a short equilibration run was performed for
	a
	duration of \SI{1}{ns} with an integration time-step of \SI{1}{fs}. Afterwards,
	each production run was calculated to a duration of \SI{40}{ns} with an
	integration time-step of \SI{2}{fs}. TIP3P water
	model\cite{Neria1996,Jorgensen1983} was employed on the
	simulation with CHARMM36 force-field, while SPC/E\cite{Berendsen1987} was
	employed on simulations
	with Berger and Gromos53A6 force-fields. The same initial configuration was
	employed to test each force-field, and it was generated using software
	Packmol\cite{Martinez2009} arranging a bilayer with composition in the same
	proportion as the membrane mimetic in table \ref{tab:mimetic_composition}, to a
	total of 9613 molecules. The phospholipid mixture was simulated as a mixture of
	39\%
	PLPC\footnote{1-palmitoyl-2-linoleoyl-\textit{sn}-glycero-3-phosphocholine},
	26\% DLPC\footnote{1,2-dilinoleoyl-\textit{sn}-glycero-3-phosphocholine}, 24\%
	DLPE\footnote{1,2-dilinoleoyl-\textit{sn}-glycero-3-phosphoethanolamine} and
	11\% DOPE\footnote{1,2-dioleoyl-\text{sn}-glycero-3-phosphoethanolamine}. These
	proportions were chosen in accordance with the composition of the phospholipid
	mixture employed, as
	reported by the vendor.\\
	PMF calculations were performed employing the Umbrella Sampling/WHAM
	method\cite{Kumar1992}. The starting configuration of each simulation window
	employed for the PMF calculation was generated from a trajectory of the target
	molecule pulling away from the center of the bilayer, making a starting point
	each \SI{1.5}{\angstrom}, up to \SI{45}{\angstrom} making a total of 30 simulation
	windows. Each simulation window was calculated with the same parameters as the
	calibrated model shown ahead, up to a total of \SI{20}{ns} on each window, with
	a weak harmonic force with constant
	\SI{240}{\kilo\joule\per\mole\per\nano\meter\squared} applied on the bilayer
	in order to maintain its shape and position during the course of each
	simulation window.\\

@@

	Another condition that the mimetic must fulfill, is that the diamagnetic susceptibility of the mesophase of the mimetic must be anisotropic so it can orient itself when exposed to an external magnetic field. This is so the
  deuterated probes in the mimetic can produce a \textit{quadrupole splitting}
  in a solution $^2$H-RMN spectrum, which will be used to calibrate the MD
  simulations. This calibrated simulation can be used to assess other
  properties, not possible to measure experimentally, with more
	confidence.\\

@@

	In order to obtain more reliable information from a molecular dynamic
	simulation,
	it is desirable that experimentally measured properties are well reproduced by
	calculations. That said, MD has to be calibrated to reproduce known experimental
	results, which is why
	we
	tested multiple force-fields to see which one yields a closer representation of
	the aliphatic chain dynamics, evidenced by reproducing $^2$H-RMN quadrupole
	splittings. Figure \ref{fig:reference}-A shows the $^2$H-NMR spectrum of the
	membrane mimetic prepared according to the composition stated in table
	\ref{tab:mimetic_composition}, enriched with \ce{D2O}(0.5\% of the total
	\ce{H2O} replaced by \ce{D2O}) and SDS-d$_{25}$(10\% of the total SDS replaced
	by SDS-d$_{25}$). The quadrupolar splitting of each C-D bond depends largely on
	their order parameter ($S_{CD}$, see equation \ref{eq:splitting}), therefore it
	makes sense to assign each quadrupolar splitting from the least ordered to the
	most ordered methylene, resulting as follows: The central signal arises from an
	average in time of HDO oriented at the interface in fast exchange with
	non-oriented HDO at the bulk (smallest splitting, \SI{388}{Hz}. Not shown). The
	next less split signal arises from the deuterated methyl group (\ce{CD3}-)
	capping the tail of each SDS-d$_{25}$, as the rotation of this group produces a
	lower order parameter, the smallest along the chain. The rest of the more split
	signals correspond to subsequent deuretated methylenes (-\ce{CD2}-), with the
	ones closer to the charged sulphate head-group having a higher quadrupolar
	splitting, since the strong Coulombic interaction between this charged end and
	the interface produces a restraining effect on the movement of the nearby
	deuterons. The adjustment of the simulation relies on the accurate reproduction
	of these quadrupolar splittings from SDS-d$_{25}$, as they reflect the dynamics
	of the lipid chains in the bilayer.\par
	\begin{figure}[h]
		\centering
		\includegraphics[width=\columnwidth]{nmr_reference.pdf}
		\caption{$^2$H-NMR spectrum of: (A) membrane mimetic enriched with SDS-d$_{25}$.
			Central peak (not shown completely) belongs to \ce{HDO} present in the
			sample, while the rest of the signals are split SDS-d$_{25}$ signals which
			were used as reference to calibrate a computational model. (B) DMPC/DHPC bicelle with added cholesterol and polyinsaturated phospholipids and enriched with DMPC-d$_{54}$ (R.E. Minto \textit{et al.}, Chem. Phys. Lipids 132 (2004) 55–64)}
		\label{fig:reference}
	\end{figure}
	Initially,
	three force-fields with different partial charge distributions were tested.
	These force-fields were chosen due to their ability to reproduce other
	structures of
	SDS aggregates\cite{Tang2014}.\par
	The tested force-fields were:
	\begin{itemize}
		\item CHARMM36\cite{Vanommeslaeghe2009} with partial charge distribution according to its own parameters.
		\item Berger\cite{Berger1997} with partial charge distribution according to
		Merz-Kollman
		method\cite{Besler1990}
		\item Berger with partial charge distribution according to
		Gromos53A6\cite{Oostenbrink2004}
		parameters.
		\item Gromos53A6 with partial charge distribution according to Merz-Kollman
		method.
		\item Gromos53A6 with partial charge distribution according to its own
		parameters.
	\end{itemize}

@@

	Further improvement to the fitting of predicted splittings was done by
	employing
	two thermostats in the simulation, one governing the bulk solution with a
	reference temperature of \SI{310}{K} and another governing the bilayer
	components with a reference temperature of \SI{320}{K}, a little higher to
	introduce more kinetic energy to the chains. The reasoning behind
	this decision was based on the expectation that increased velocity on the
	bilayer components would have a greater effect on the mobility towards the
	center on the bilayer rather than in the interface, where Coulombic
	interactions
	are stronger and have a restraining effect on the mobility of the interface.
	After
	this adjustment, the simulation results in predicted quadrupolar splittings in
	very good agreement with the experimental ones, as shown in figure
	\ref{fig:2nd_calibration}.

@@

	Polarized light microscopy of the mesophase shows a thread-like pattern, this
	is
	characteristic of a lyotropic nematic phase\cite{dierking2006textures}.
	Furthermore, considering the magnitude of the measured quadrupolar
	splittings, and the fact that each methylene's deuteron pair in SDS-d$_{25}$
	yields
	a
	single quadrupolar splitting in solution $^2$H-NMR (see figure
	\ref{fig:reference}-A), we can conclude that this phase has a bilayer
	like structure with its bilayer normal perpendicular
	to the magnetic field ($\theta=\pi/2$ in eq. \ref{eq:splitting}). The
	posibility of a calamitic phase is discarded, since a calamitic phase implies a
	director axis being parallel to the magnetic field ($\theta=0$ in eq.
	\ref{eq:splitting}) which would produce splittings considerably smaller than
	observed. Regarding the size of the aggregate, cryo-TEM imagery of similar
  bicelles (made with TTAC\footnote{Trimethyltetradecylammonium chloride} instead of SDS)
  results in aggregates of about
  \SI{2}{nm}-\SI{5}{nm}\cite{Ruiz-Fernandez2016}, and we expect for the size of
  the membrane mimetic aggregate to be in the same order of magnitude.\\
   When comparing the NMR spectrum of this bicelle (figure \ref{fig:reference}-A) with one taken from a DHPC/DMPC bicelle with cholesterol and polyinstaturated phospholipids (figure \ref{fig:reference}-B)\cite{Minto2004}, one can see that DMPC-d$_{54}$ splittings (and hence order parameters) are similar to the splittings in SDS-d$_{25}$, therefore one can conclude that the orientational dynamics of this SDS-containing mimetic are similar to a mimetic made from purely phospholipid.\\

@@

	When studying the
	effects of adding \SI{7}{mg} of Levodopa per gram of membrane mimetic enriched
	with SDS-d$_{25}$, the effects are minor to negligible (see figure
	\ref{fig:sds_benzocaine}),
	implying that Levodopa is unable to enter the bilayer to alter
	the dynamics of the aliphatic chains.\\
	Employing the same method as in Benzocaine, a PMF profile was calculated for
	the
	process of Levodopa permeating the membrane mimetic (figure
	\ref{fig:levodopa_profile}). This profile shows that the lowest
	energy location for Levodopa to be in, is outside the hydrophobic bilayer, alongside the
	Stern
	layer.
	It also shows that in order to permeate the interface to translocate through
	the mimetic, Levodopa requires a rather
	large activation energy (\SI{102.4}{\kilo\joule\per\mol}), showing that a
	passive permeation of Levodopa mechanism is actually not possible at
	physiological temperature, as confirmed by $^2$H-NMR spectra. 
	\begin{figure}[htb]
		\centering
		\includegraphics[width=\columnwidth]{ldopa_profile_density}    
		\caption{Mean force potential profile for the process of Levodopa
			translocating through a membrane mimetic. The blue dotted area represents
			the water particle density, while the smooth orange area represents the
			lipid particle density in the simulation.}
		\label{fig:levodopa_profile}
	\end{figure}
